An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-08-25 CMPSpaper_writing/CMPSpaper_writing.Rmd
modified result section for hamby 252

$$
V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }
$$

@@

As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252 \wj{to the best of our knowledge} ). In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44. \wj{For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data}: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures. \wj{More details and code can be found in the Appendix.} Note that researchers of @cmps \wj{applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.} However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.

@@

\autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy. Although the CMPS scores we found here are not exactly the same as those presented in @cmps since we don't have the exact parameters and functions used by the researchers, the results we obtained qualitatively agree with their results. For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM).

The parameters we used in `extract_feature_cmps` are:

@@

Note that for Hamby set 252, one unit represents 1.5625 \textmu m so setting `seg_length = 50` makes each basis segment have length 78.125 \textmu m. And `Tx = 25` makes the tolerance zone be $\pm 39.0625$ \textmu m. This is to mimic the parameters used in @cmps.

>>>>

\begin{align}
V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }
\end{align}

@@

As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252 \wj{to the best of our knowledge} ). In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44. \wj{For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data and include code in the appendix}: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures. Note that researchers of @cmps \wj{applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.} However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.

@@

\autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy. The parameters we used in `extract_feature_cmps` for the CMPS algorithm are:

@@

As noted above, the CMPS scores we found here are not exactly the same as those presented in @cmps since we were not able to follow their framework, but the results presented in \autoref{fig:result1_252} are qualitatively equivalent to those presented in @cmps, showing a clear separation between the known matching comparisons (KM) group and the known non-matching comparisons (KNM) group for both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.

Additionally, to mimic the parameters used in @cmps, we set `seg_length = 50` and `Tx = 25` to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu for Hamby set 252).

The sum of squares ratios are 20.85 and 29.32 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively. \wj{TODO: add some comments following this result}

```{r, echo=FALSE, eval=FALSE}
with(CMPS_hamby252_results$cmps.table[[2]], {
  tibble(cmps.max.m, cmps.maxbar.m) %>% 
    apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
})
```
